---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(lubridate)
library(zoo)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)
library(kableExtra)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)
```

```{r}

JonsData <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/newCensusDatatoBeAnalyzed.csv", header = T, stringsAsFactors = F)
```


```{r}
JonsData1 <- JonsData %>% mutate(App.Application.Date = as.Date(App.Application.Date, format = "%m/%d/%Y"))

```

```{r eval=FALSE, include=FALSE}
Joined_N <- JonsData1 %>% 
  select(Last.Name,  City, State,  App.Application.Date) 

Joined_N <- Joined_N %>% 
  mutate(Month = as.yearmon(App.Application.Date))

Joined_N <- Joined_N %>% mutate(
  Mo = month(Month), 
  Yr = year(Month)) %>% 
  group_by(Month, Mo, Yr) %>% 
  summarise(Apps = n())

Joined_N <- Joined_N %>% select(Month, Apps)

OldData <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/LastYearData.csv", header = T, stringsAsFactors = F)

kable(OldData, caption = "Last Year") %>%
#   
#   kable_styling(full_width = FALSE, position = "float_left")
# 
# 
# 
# kable(Joined_N, caption = "This Year") %>%
#   kable_styling(full_width = FALSE, position = "left")

Joined_N <- Joined_N %>% mutate(Month = as.character(Month))

UTDData_DeletedDups <- rbind.data.frame(OldData, Joined_N)
UTDData_DeletedDups[20,3] <- 5

UTDData_DeletedDups <- UTDData_DeletedDups %>% mutate(Month = as.yearmon(Month, format = "%b %Y")) %>% na.omit()
write.csv(UTDData_DeletedDups, "C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/TidiedDataAll.csv", row.names = F)

  
```

```{r}
Data <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/TidiedDataAll.csv", header = T, stringsAsFactors = F)
```

# __FY21 Analytics Project Template__

# Description


`r newthought('FY20 saw an increase')` in applications for students seeking online programs. In general,
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.



```{r fig.height=3, fig.width=8}
SoilSciGuylabs <- c("July", "August", "September", "October", "November", "December", "January", "February", "March", "April" ,"May", "June")


#kable(Data %>% select(Fiscal.Year, everything()))
ggplot(Data, aes(Fiscal.Month.Number.Starting.in.July,
                Applications.for.Online.Programs, group=Fiscal.Year, colour=Fiscal.Year))+
  geom_line(size=2) +
  #geom_point() +
  labs(x="Month", colour="Year") +
  theme_classic()+  
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10,11,12),labels= c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr" ,"May", "Jun"))+ theme(axis.text.x = element_text(angle = 45))+ scale_color_manual(values=c("#0e1033", "#731012", "#f5a800","#60c7d1"  ))

# ggplot(Data, aes(x = factor(Fiscal.Month.Number.Starting.in.July), y = Applications.for.Online.Programs, color = factor(Fiscal.Year))) + geom_line())
```

```{r fig.height=3, fig.width=8}
Data <- Data %>% mutate(DATE = as.Date(DATE, format = "%m/%d/%Y"))
ggplot(Data, aes(x = DATE,
                Applications.for.Online.Programs))+
  geom_line(size=2) +
  #geom_point() +
  labs(x="Date") +
  theme_classic()+  
  scale_x_date(date_labels = "%b/%y", date_breaks = "3 month",
               date_minor_breaks = "1 years") +
  xlab("") + 
  ylab("Applications")+
  theme(axis.text.x = element_text(angle = 45))
#+ scale_color_manual(values=c("#60c7d1", "#ccdf7f", "#f5a800", "#0e1033" ))
```


# Findings


# Conclusions

 
* Facebook has not published benchmarks for this platform. View and completion rates are \textcolor{red}{slightly down} from this same quarter FY19, but the website has far more unique pageviews.

* In general,
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.

* Two

\href{https://www.wrike.com/open.htm?id=525346252}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/fy20_cybersecurity}{{\color{blue}{\underline{Github Repository}}}}

```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```





```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
