---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(lubridate)
library(zoo)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)
library(kableExtra)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)
```

```{r fig.height=3, fig.width=8}

JonsData <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/newCensusDatatoBeAnalyzed.csv", header = T, stringsAsFactors = F)
```


```{r}
JonsData1 <- JonsData %>%  mutate_at(
    vars("Birthdate", "App.Application.Date"), 
    as.POSIXct,
    format = "%m/%d/%Y") %>%
  mutate(AgeAtInquiry = round(difftime(App.Application.Date, Birthdate, units = "weeks"),0), 
                        Age_Y = as.integer(round(AgeAtInquiry/52, 0)), 
                        
                        AgeGroup = 
                          ifelse(Age > 13 & Age_Y <=19, "19 and Under", 
                                 ifelse(Age_Y > 19 & Age_Y < 25, "20-25", 
                                        ifelse(Age_Y >= 25, "26 and Up", "Unknown"))), 
                        AgeGroup = ifelse(is.na(AgeAtInquiry) , "Unknown", AgeGroup), 
         
  FiscalYear = ifelse(App.Application.Date >="2015-07-01" & App.Application.Date <= "2016-06-30", "FY16", 
                      ifelse(App.Application.Date>="2016-07-01" & App.Application.Date <= "2017-06-30", "FY17",
                             ifelse(App.Application.Date>="2017-07-01" & App.Application.Date <= "2018-06-30", "FY18",
                                    ifelse(App.Application.Date>="2018-07-01" & App.Application.Date <= "2019-06-30", "FY19",
                                           ifelse(App.Application.Date>="2019-07-01" & App.Application.Date <= "2020-06-30", "FY20",
                                                  ifelse(App.Application.Date>="2020-07-01" & App.Application.Date <= "2021-06-30", "FY21","FY15 or earlier"))))))) %>% 
  count(FiscalYear, AgeGroup) %>% rename(Applications = n) %>% na.omit()

  

```

```{r eval=FALSE, include=FALSE}
# Joined_N <- JonsData1 %>% 
#   select(Last.Name,  City, State,  App.Application.Date) 
# 
# Joined_N <- Joined_N %>% 
#   mutate(Month = as.yearmon(App.Application.Date))
# 
# Joined_N <- Joined_N %>% mutate(
#   Mo = month(Month), 
#   Yr = year(Month)) %>% 
#   group_by(Month, Mo, Yr) %>% 
#   summarise(Apps = n())
# 
# Joined_N <- Joined_N %>% select(Month, Apps)
# 
# OldData <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/LastYearData.csv", header = T, stringsAsFactors = F)
# 
# #kable(OldData, caption = "Last Year") %>%
# #   
# #   kable_styling(full_width = FALSE, position = "float_left")
# # 
# # 
# # 
# # kable(Joined_N, caption = "This Year") %>%
# #   kable_styling(full_width = FALSE, position = "left")
# 
# Joined_N <- Joined_N %>% mutate(Month = as.character(Month))
# 
# UTDData_DeletedDups <- rbind.data.frame(OldData, Joined_N)
# UTDData_DeletedDups[20,3] <- 5
# 
# UTDData_DeletedDups <- UTDData_DeletedDups %>% mutate(Month = as.yearmon(Month, format = "%b %Y")) %>% na.omit()
# # write.csv(UTDData_DeletedDups, "C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/TidiedDataAll.csv", row.names = F)

  
```

```{r}
Data <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/TidiedDataAll.csv", header = T, stringsAsFactors = F)
```


# Description

`r newthought('The purpose of this analysis')` is to explore the changes that have occurred in the flow of applications to Undergraduate Online Programs. I look at both application data from past census reports and inquiry data from prospective students who fill out Marketing inquiry forms that can be filled out from campaign landing pages.



    

# Findings


`r newthought('FY20 saw an increase')` in applications for students seeking online programs. After a one year period that started in Aug, 2018, marking a dearth of applications to the University's Undergraduate Online Programs, applications started coming in at a higher rate. This change is evident in the two plots below. 

The first shows that there has been growth in the last census year.

# 

```{r one, fig.height=3, fig.width=8}
SoilSciGuylabs <- c("July", "August", "September", "October", "November", "December", "January", "February", "March", "April" ,"May", "June")


#kable(Data %>% select(Fiscal.Year, everything()))
ggplot(Data, aes(Fiscal.Month.Number.Starting.in.July,
                Applications.for.Online.Programs, group=Fiscal.Year, colour=Fiscal.Year))+
  geom_line(size=2) +
  #geom_point() +
  labs(x="Month", colour="Year") +
  theme_classic()+  
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10,11,12),labels= c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr" ,"May", "Jun"))+ 
  theme(axis.text.x = element_text(angle = 45))+ scale_color_manual(values=c("#0e1033", "#731012", "#f5a800","#60c7d1")) +
  ggtitle("Year Over Year Application Growth for Online Undergraduate Programs ")


```

The second plot, shown below, captures the same data on a time line. The second period of activity, from August 2019, is significantly higher that the previous period. This is very exciting.

#

```{r two, fig.height=3, fig.width=8}
Data <- Data %>% mutate(DATE = as.Date(DATE, format = "%m/%d/%Y"))
ggplot(Data, aes(x = DATE,
                Applications.for.Online.Programs))+
  geom_line(aes(color = "blue"), size = 1.1) +
  #geom_point() +
  labs(x="Date") +
  theme_classic()+  
  scale_x_date(date_labels = "%b/%y", date_breaks = "6 month",
               date_minor_breaks = "1 years") +
  xlab("") + 
  ylab("Applications")+
  theme(axis.text.x = element_text(angle = 45))+ 
  scale_color_manual(values=c("#f5a800")) + ggtitle("Flow of Applications for Undergraduate Online Programs: July 2017 - October 2020 ")+ theme(legend.position = "none") 
```


The final plot, shown below, marks the flow of marketing inquiry forms (as an initial referral source). What is clear is an increase in the flow of inquiries preceded the growth in applications. 

#

```{r three, fig.height=3, fig.width=8}
MarketingForms <- read.csv("C:/Users/christine.iyer/Box/FY20 SpecialProjects/FlowOfApps_OnlinePrograms/Data/MarketingInquiryForms.csv", header = T, stringsAsFactors = F)

MarketingForms1 <- MarketingForms %>% 
  mutate(Initial.Source.Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"),
         DateMY = as.yearmon(Initial.Source.Date), 
         DateMY = as.Date(DateMY, format = "%b %Y")) %>% 
  count(DateMY) %>% 
  filter(DateMY >= "2017-07-01") 
MarketingForms2 <- MarketingForms1 %>% 
  rename(MarktingInquiryForms = n)
  
plot <- ggplot(MarketingForms2, aes(x=DateMY, y=MarktingInquiryForms))
  plot + (geom_line(aes(color = "blue"), size = 1.1)) +
  theme_classic()+ 
  scale_x_date(date_labels = "%b/%y", date_breaks = "6 month",
               date_minor_breaks = "6 months")+ 
    theme(axis.text.x = element_text(angle = 45))+
    
  scale_color_manual(values=c("#f5a800"))+ 
    xlab("")+
    ylab("Marketing Inquiry Forms")+ 
    ggtitle(" Initial Inquiries by Marketing Forms for Undergraduate Online Programs")+ theme(legend.position = "none") 
    
```

Age of Applicant

```{r Jons}
kable(JonsData1) 
```


# Conclusions

 
* While a small component of the University's portfolio of products, Online Programs have grown. 

* Further analysis into the the performance of ads for the online programs might show a similar trend. 

\href{https://www.wrike.com/open.htm?id=589938175}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/online-programs-application-flow}{{\color{blue}{\underline{Github Repository}}}}

```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```





```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
